---
title: "Code Replication"
author:  "Prathishta"
date: 07-10-2024
description: "This is the replication code for the new dataset I am trying to work with"
---

## Introduction

For Assignment 1 (A1), I am working with a dataset titled "Books Banned in the USA." In this analysis, I will initiate the necessary packages, explore the dataset, clean it up, and then provide summary statistics to gain insights.

## Initiating packages

```{r}
#| label: setup
library (tidyverse)
library (ggformula)
library (mosaic)
library (kableExtra)

```

I have initiated the packages that may be necessary for this analysis.

## Looking into the data set "Books Banned in the USA"

```{r}
banned_books



```

## Summary Overviews

```{r}
 glimpse(banned_books)
 inspect(ba
```

```{r}
skimr::skim ("banned_books")

```

## Data Inspection

If the initial skim does not give much information, I will further explore the structure of the dataset:

```{r}
# Checking
glimpse(banned_books)
str(banned_books)

# Viewing the first and last few rows
head(banned_books)
tail(banned_books)

# Dimensions of the dataset
dim(banned_books)

# Summary statistics of the dataset
summary(banned_books)

```

## Data Cleaning

To enhance the dataset for analysis, I will clean it by trimming whitespace from character columns and converting character columns to numeric where applicable:

```{r}
banned_books <- banned_books %>%
  mutate(across(where(is.character), trimws),  
         # Trimming whitespace from character columns
         across(where(is.numeric), as.numeric)) 
# Converting chr columns to num

```

## Re-assessing Data

After cleaning the dataset, I will re-run the skim function to check if the cleaning process has improved the data.

```{r}
skimr::skim(banned_books)

```

## Summarizing the Banned Books Dataset

```{r}
# Group by "State" and "Type of Ban" and summarize the dataset
banned_books_summary <- banned_books %>%
  group_by(State, `Type of Ban`) %>%
  summarize(
    count = n(),                    
    # Count number of entries per group
    unique_authors = n_distinct(Author) 
    # Count unique authors
  )

# Print the summary
print(banned_books_summary)

```

```{r}
# Load necessary libraries
library(dplyr)

# Load the dataset
banned_books <- read.csv("C:/Users/prath/Documents/My R/my blog/A1/data/banned.csv.csv")


```
