---
title: "Counts"
author: "Prathishta"
date: 07-10-2024
description: ""
---

## Introduction

I will be exploring dataset on banned books by counting categories like the number of bans, type of bans,etc.

## Count Banned Book by state

```{r}
banned_books
```

```{r}
# Load necessary libraries
library(dplyr)

# Count number of bans per state
bans_by_state <- banned_books %>%
  group_by(State) %>%
  summarise(count = n()) %>%
  arrange(desc(count))

# Display the count
print(bans_by_state)
```

## Count of Banned books by Author

The number of books challenged or removed by each author, this gives information of authors that are facing censorship.

```{r}
# Load necessary libraries
library(dplyr)
library(ggplot2)

# Check the data structure
print(head(banned_books))
print(str(banned_books))

# Count number of books by Author
author_count <- banned_books %>%
  group_by(Author) %>%
  summarise(count = n(), .groups = 'drop') %>%
  arrange(desc(count))

# Plotting the count of banned books by Author
ggplot(author_count %>% top_n(10), aes(x = reorder(Author, count), y = count)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  labs(title = "Top 10 Banned Books by Author", x = "Author", y = "Count") +
  theme_minimal() +
  theme(axis.text.y = element_text(size = 10))

```

## Count by type of ban

The Type of ban column categorizes books based on how they were banned ,Let's count the occurrences of each type of ban.

```{r}
# Count number of books by Type of Ban
type_count <- banned_books %>%
  group_by(`Type of Ban`) %>%
  summarise(count = n()) %>%
  arrange(desc(count))

# Display the counts
print(type_count)

# Plotting the count of books by Type of Ban
ggplot(type_count, aes(x = reorder(`Type of Ban`, count), y = count)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  labs(title = "Number of Banned Books by Type of Ban", x = "Type of Ban", y = "Count") +
  theme_minimal()



```

## Count by Origin of Challenge

I am going to count how many books were challenged and how.

```{r}
# Load necessary libraries
library(ggplot2)
library(dplyr)

# Count by 'Origin of Challenge'
origin_of_challenge_count <- banned_books %>%
  group_by(`Origin of Challenge`) %>%
  summarise(count = n()) %>%
  arrange(desc(count))

# Create a pie chart
ggplot(origin_of_challenge_count, aes(x = "", y = count, fill = `Origin of Challenge`)) +
  geom_bar(stat = "identity", width = 1) +
  coord_polar("y", start = 0) +
  labs(title = "Distribution of Banned Books by Origin of Challenge", 
       fill = "Origin of Challenge") +
  theme_void() + 
  theme(legend.position = "right") 
# Adjust position





```
